# Data

## Sources

### Crime Data from 2020 to Present

[Los Angeles Open Data](<https://data.lacity.org/Public-Safety/Crime-Data-from-2020-to-Present/2nrs-mtv8>[)](%5Bhttps://clio.columbia.edu/))](<https://clio.columbia.edu/>)))

The data was collected by the Los Angeles Police Department, LAPD. It reflects incidents of crime since 2020. The data inside is transcribed from the official crime report, and is typed from the paper, which means that there might be typos and inaccuracies.

\- Collected by Los Angeles Police Department, LAPD

\- Owner: LAPD OpenData

\- Date created: February 10, 2020

\- Last Updated: November 2, 2022

**Data Format:**

\- CSV file

\- 595K rows and 28 columns

\- Three types of data: Plain text, Number, date

\- Update Frequency: weekly

\- Columns: Date occurring, area, criminal code, victim age, victim sex, weapon description, status, location, etc.

\- Each row is a crime incident

**Issues:**

-   Some columns like crime codes are extremely sparse, containing lots of missing values

-   We need to spend tons of time on data cleaning. There are many categorical columns, which require some string transformation. And some other columns carry geographical information, so we should merge these columns to extract an exact location.

-   For some text columns, the data inside are mostly abbreviations or codes, which cannot be directly used. In this case, we need to do some research and replace these codes with suitable formats that can be understood easily.

-   Since there are about 600k datapoints, it is possible that two datapoints will overlap with each other. In this case, we may try convert it into log scale, or sample certain amount of datapoints, instead of using all of them.

**Plan to import:**

1.  Download the csv file from the website

2.  Preprocess data for convenience :

    -   Replace columns containing spaces such as "DATE OCC" to "DATA_OCC"

    -   Remove character "-"

3.  We plan to import the csv data into MySQL database deployed on the server and visit these data through `odbc` package, so that it might be easier to collaborate on data.

**Contact data owner:**

On the dataset webpage(Link is attached on the top of the file), click the "Contact Dataset Owner" button to ask a question, make a comment, or point out something about the data.


### Area size of each community(Supplementary Dataset)

[lapdonline.org](https://www.lapdonline.org)

-   https://www.lapdonline.org/lapd-contact/south-bureau/77th-street-community-police-station/

-   https://www.lapdonline.org/lapd-contact/central-bureau/central-community-police-station/

-   https://www.lapdonline.org/lapd-contact/valley-bureau/devonshire-community-police-station/

-   https://www.lapdonline.org/lapd-contact/valley-bureau/foothill-community-police-station/

-   https://www.lapdonline.org/lapd-contact/south-bureau/harbor-community-police-station/

-   https://www.lapdonline.org/lapd-contact/central-bureau/hollenbeck-community-police-station/

-   https://www.lapdonline.org/lapd-contact/west-bureau/hollywood-community-police-station/

-   https://www.lapdonline.org/lapd-contact/valley-bureau/mission-community-police-station/

-   https://www.lapdonline.org/lapd-contact/valley-bureau/north-hollywood-community-police-station/

-   https://www.lapdonline.org/lapd-contact/central-bureau/

-   https://www.lapdonline.org/lapd-contact/central-bureau/northeast-community-police-station/

-   https://www.lapdonline.org/lapd-contact/west-bureau/

-   https://www.lapdonline.org/lapd-contact/west-bureau/pacific-community-police-station/

-   https://www.lapdonline.org/lapd-contact/central-bureau/rampart-community-police-station/

-   https://www.lapdonline.org/lapd-contact/south-bureau/southeast-community-police-station/

-   https://www.lapdonline.org/lapd-contact/south-bureau/southwest-community-police-station/

-   https://www.lapdonline.org/lapd-contact/valley-bureau/

-   https://www.lapdonline.org/lapd-contact/valley-bureau/van-nuys-community-police-station/

-   https://www.lapdonline.org/lapd-contact/west-bureau/west-los-angeles-community-police-station/

-   https://www.lapdonline.org/lapd-contact/valley-bureau/west-valley-community-police-station/

-   https://www.lapdonline.org/lapd-contact/west-bureau/wilshire-community-police-station/


**Data Format:**

-   The area size data is written in text format on the website of LAPD division.

-   Two variables: area, size.

-   2 rows, 21 columns, each row is an area name with its corresponding size(unit: square miles)

**Issues:**

-   There are three division(communities), which were added in recent years and do not have a area size data on its website. They are Newton division from central bureau, Olympic division from west bureau and Topanga division in valley bureau

**Plan to import:**

Browse all webpages and manually enter the data into a csv table.


## Cleaning / transformation

### Crime Data from 2020 to Present

A tidy data set has one observation in each row, and the variable we are interested in is Mocodes, which are the activities associated with crime. We split rows with multiple Mocodes, so that each line contains only one Mocode, representing an observation. We write a simple python script to do this.

### Area size of each community

The data collected directly from text on the websites lacks information on the area of the three divisions (Newton, Olympic and Topanga). But fortunately, those three divisions belong to three different bureaus, and on the official websites of these bureaus, the total area of all divisions under a certain bureau is shown. 

We can get the area of these three unknown communities(divisions) by subtracting the area of the other known divisions in the same bureau from the total area in that bureau,and add this value to our table.

## Missing value analysis

In our dataset, there actually contain lots of missing values, and they mostly concentrate on a few specific columns. Hence, in this section, we will visualize these missing values.

```{r}
# import data
df <- read.csv("Data/clean/Crime_Data_from_2020_to_Present_column_modified_zys1.csv")
```

```{r}
#number of missings by graph
library(naniar)
gg_miss_upset(df,nsets = n_var_miss(df))
```

From the graph above, we can observe the missing patterns in this dataset. To be specific, there are about 10 kinds of missing patterns in total. The missing values are mostly concentrated on four columns: Weapon_used,Crm_cd_2,Crm_cd_3, and Crm_cd_4. The most common missing pattern is that these four columns are all missed. The occurrences of this pattern exceed more than half of the dataset. The second most common missing pattern is that the crime codes 2,3,4 are all missing, which consists 1/3 of the dataset. Furthermore, by taking a closer look at the missing patterns, we can see that the "crm_cd_4" nearly appears in all the patterns, which means that it may have the highest number of missing values.

```{r}
library(gridExtra)
library(ggplot2)

g1<-gg_miss_span(df, Weapon_Used_Cd, span_every = 30000) +
  ggtitle("Propo of missing in Weapon")

g2<-gg_miss_span(df, Crm_Cd_2, span_every = 30000)+
  ggtitle("Prop of missing in Crm_2")

g3<-gg_miss_span(df, Crm_Cd_3, span_every = 30000)+
  ggtitle("Prop of missing in Crm_3")

g4<-gg_miss_span(df, Crm_Cd_4, span_every = 30000)+
  ggtitle("Prop of missing in Crm_4")

grid.arrange(g1,g2,g3,g4, nrow = 2)
```

From the previous graph, we conclude that the missing value are mostly concentrated on these four columns. Thus, this graph displays the proportion of missing values in these four columns. Specifically, we can see that the values in columns Crm_cd_3 and Crm_cd_4 are completely missed. For weapon_used, it has about 60% of missing values, while Crm_cd_2 has 95% of missing data.